We are not the 99 percent: quantifying asphericity in the Local Group satellites' distributions

### 2017-11-04 paper/paper.tex
without mu data and plots

\section{Results from ELVIS}
\begin{figure*}
\centering
\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.24\textwidth]{scatter_ranked_elvis_mu.pdf}
\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_width.pdf}
\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.24\textwidth]{scatter_norm_ranked_elvis_mu.pdf}
\caption{ELVIs results for the quantities presented for the Illustris-1
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio} and
  \ref{fig:scatter_mu}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

>>>>

\section{Results from ELVIS}
\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
\caption{ELVIs results for the quantities presented for the Illustris-1
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}
